West Africa cuckoo stopover rainfall patterns

### 2018-07-11 stopover_rainfall_ndvi_detailcoords_vis.Rmd
Added NDVI anomaly values to plot

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
    geom_line(data=t2, aes(x=variable, y=value2*500), colour='red')+
  geom_line(data=t2, aes(x=variable, y=aquaNDVI*500), colour='cyan')+
  geom_line(data=t2, aes(x=variable, y=terrNDVI*500), colour='orange')+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding))+geom_label(data=lc1, aes(x=15, y=450, vjust=1,label=label), fill=NA)

>>>>

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
    geom_line(data=t2, aes(x=variable, y=value2*500), colour='red')+
  geom_line(data=t2, aes(x=variable, y=aquaNDVI*500), colour='cyan')+
  geom_line(data=t2, aes(x=variable, y=terrNDVI*500), colour='orange')+
    geom_line(data=t2, aes(x=variable, y=aquaANOM*1000+200), colour='cyan', linetype=2)+
    geom_line(data=t2, aes(x=variable, y=terrANOM*1000+200), colour='orange', linetype=2)+
  geom_hline(yintercept=200)+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding))+geom_label(data=lc1, aes(x=15, y=450, vjust=1,label=label), fill=NA)
